### 2014-09-28 rebuttal.md

	*Fixed*

>Validity of the findings

>Major comments:

8. The authors mention calculating the site frequency spectrum for their data in line 133, did anything come of this analysis?

	*This SFS analysis was done as part of the calculation of Tajima's D. Nothing per se was done with the SFS itself.*

9. Is anything known about the demographic history of this population? As the authors acknowledge, the patterns used to infer selection according to Tajima's D can also be produced from demographic events and the authors should provide any data that exists on the population history. If this data does not exist the authors should state that this and include demography as a possible explanation of their data in their conclusions about tables 3 and 4.

	*Nothing specific is known of these populations, other than what can be inferred from paleo-climate models of desert expansion over the last 10k years. I have added a claus in the interpretation of Tajima's D to reflect the possibility that demography may impact these metrics. Line 257*

### 2014-09-28 Pero_Transcriptome.tex
further

In addition to this, we estimated mean TPM (number of transcripts per million) for all transcripts. {\hypertarget{Table 2}{Table 2}} consists of the 10 genes whose mean TMP was the highest. Several genes in this list are predominately  present in a single tissue type. For instance Transcript\_126459, Albumin is very highly expressed in the liver, but less so in the other tissues. It should be noted, however, that making inference based on uncorrected values for TPM is not warranted. Statistical testing for differential expression was not implemented due to the fact that no replicates are available.  \\

@@

The distribution of the estimates of Tajima's D for all of the assembled transcripts is shown in Figure 2. The distribution is skewed toward negative values (mean=-0.89, variance=0.58), which is likely the result of purifying selection, a model of evolution commonly invoked for coding DNA sequences \citep{Chamary:2006db}. \hyperlink{Table 3}{Table 3} presents the 10 transcripts whose estimate of Tajima's D is the greatest, while \hyperlink{Table 4}{Table 4} presents the 10 transcripts whose estimate of Tajima's D is the least. The former list of genes is likely to contain transcripts experiencing balancing selection in the studied population. This list includes, interestingly, genes obviously related to solute and water balance (e.g. Clcnkb and a transmembrane protein gene) and immune function (a interferon-inducible GTPase and a Class 1 MHC gene). The latter group, containing transcripts whose estimates of Tajima's D are the smallest are likely experiencing purifying selection. Many of these transcripts are involved in core regulatory functions where mutation may have strongly negative fitness consequences. \\

>>>>

In addition to this, we estimated mean TPM (number of transcripts per million) for all transcripts. {\hypertarget{Table 2}{Table 2}} consists of the 10 genes whose mean TPM was the highest. Several genes in this list are predominately  present in a single tissue type. For instance Transcript\_126459, Albumin is very highly expressed in the liver, but less so in the other tissues. It should be noted, however, that making inference based on uncorrected values for TPM is not warranted. Statistical testing for differential expression was not implemented due to the fact that no replicates are available.  \\

@@

The distribution of the estimates of Tajima's D for all of the assembled transcripts is shown in Figure 2. Although Tajima's D is known to be sensitive to demographic history, which is largely unknown for this population, the estimates may also be drive by patterns of selection. In general, the distribution is skewed toward negative values (mean=-0.89, variance=0.58), which may be the result of purifying selection, a model of evolution commonly invoked for coding DNA sequences \citep{Chamary:2006db}. \hyperlink{Table 3}{Table 3} presents the 10 transcripts whose estimate of Tajima's D is the greatest, while \hyperlink{Table 4}{Table 4} presents the 10 transcripts whose estimate of Tajima's D is the least. The former list of genes may contain transcripts experiencing balancing selection in the studied population. This list includes, interestingly, genes obviously related to solute and water balance (e.g. Clcnkb and a transmembrane protein gene) and immune function (a interferon-inducible GTPase and a Class 1 MHC gene). The latter group, containing transcripts whose estimates of Tajima's D are the smallest are likely experiencing purifying selection. Many of these transcripts are involved in core regulatory functions where mutation may have strongly negative fitness consequences. \\
